### 2013-12-17 poster_new/conference_poster_4.tex
new design for poster - more formatting 3

\documentclass[portrait,a1paper,fontscale=0.45]{baposter} % Adjust the font scale/size here

@@

\begin{poster}
{
headerborder=closed, % Adds a border around the header of content boxes
colspacing=1em, % Column spacing
%bgColorOne=white, % Background color for the gradient on the left side of the poster
bgColorOne=col1,
%bgColorTwo=white, % Background color for the gradient on the right side of the poster
bgColorTwo=col2,
borderColor=lightblue, % Border color
headerColorOne=black, % Background color for the header in the content boxes (left side)
headerColorTwo=lightblue, % Background color for the header in the content boxes (right side)
headerFontColor=white, % Text color for the header text in the content boxes
boxColorOne=white, % Background color of the content boxes
textborder=roundedleft, % Format of the border around content boxes, can be: none, bars, coils, triangles, rectangle, rounded, roundedsmall, roundedright or faded
eyecatcher=false, % Set to false for ignoring the left logo in the title and move the title left
headerheight=0.1\textheight, % Height of the header
headershape=roundedright, % Specify the rounded corner in the content box headers, can be: rectangle, small-rounded, roundedright, roundedleft or rounded
headerfont=\Large\bf\textsc, % Large, bold and sans serif font in the headers of content boxes
%textfont={\setlength{\parindent}{1.5em}}, % Uncomment for paragraph indentation
linewidth=2pt % Width of the border lines around content boxes
}
%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------
%
{\includegraphics[height=4em]{logo.png}} % First university/lab logo on the left
{\bf\textsc{Hierarchical Controller Architecture in Software Defined Networks}\vspace{0.5em}} % Poster title
{\textsc{\{ Gourav Khaneja, Sweta Seethamraju \& Praveen Kumar \} \hspace{12pt}}} % Author names and institution
{\hspace{120pt} \includegraphics[height=8em]{UIUC_logo.png}} % Second university/lab logo on the right

@@

\headerbox{METRICS}{name=metrics,column=1,below=exp}{
\begin{itemize}
\item Path length (number of hops) of the routes assigned to flows.
\item Maximum link utilization of the path assigned to flows.
\item Communication overhead (number of messages exchanged between controllers) for setting up routes for flows.   
\end{itemize}
\begin{multicols}{3}
\begin{center}
\includegraphics[scale=0.3]{msg}
\captionof{figure}{Per flow communication overhead}
\label{fig:msg}
\end{center}

\begin{minipage}{.3\textwidth}
\begin{center}
\includegraphics[scale=0.3]{path.png}
\captionof{figure}{Path length}
\label{fig:path}
\end{center}
\end{minipage}

\begin{minipage}{.3\textwidth}
\begin{center}
\includegraphics[scale=0.3]{util.png}
\captionof{figure}{Maximum link utilization}
\label{fig:util}
\end{center}
\end{minipage}
\end{multicols}

>>>>

\documentclass[portrait,a1paper,fontscale=0.4]{baposter} % Adjust the font scale/size here

@@

\begin{poster}
{
headerborder=closed, % Adds a border around the header of content boxes
colspacing=1em, % Column spacing
%bgColorOne=white, % Background color for the gradient on the left side of the poster
bgColorOne=col1,
%bgColorTwo=white, % Background color for the gradient on the right side of the poster
bgColorTwo=col2,
borderColor=lightblue, % Border color
headerColorOne=black, % Background color for the header in the content boxes (left side)
headerColorTwo=lightblue, % Background color for the header in the content boxes (right side)
headerFontColor=white, % Text color for the header text in the content boxes
boxColorOne=white, % Background color of the content boxes
textborder=roundedleft, % Format of the border around content boxes, can be: none, bars, coils, triangles, rectangle, rounded, roundedsmall, roundedright or faded
eyecatcher=false, % Set to false for ignoring the left logo in the title and move the title left
headerheight=0.1\textheight, % Height of the header
headershape=roundedright, % Specify the rounded corner in the content box headers, can be: rectangle, small-rounded, roundedright, roundedleft or rounded
headerfont=\Large\bf\textsc, % Large, bold and sans serif font in the headers of content boxes
%textfont={\setlength{\parindent}{1.5em}}, % Uncomment for paragraph indentation
linewidth=2pt % Width of the border lines around content boxes
}
%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------
%
{\includegraphics[height=4em]{logo.png}} % First university/lab logo on the left
{\bf\textsc{Hierarchical Controller Architecture in Software Defined Networks}\vspace{0.5em}} % Poster title
{\textsc{\{ Gourav Khaneja, Sweta Seethamraju \& Praveen Kumar \} \hspace{12pt}}} % Author names and institution
{\hspace{40pt} \includegraphics[height=8em]{UIUC_logo.png}} % Second university/lab logo on the right

@@

\headerbox{METRICS}{name=metrics,column=1,below=exp}{
\begin{itemize}
\item Path length (number of hops) of the routes assigned to flows.
\item Maximum link utilization of the path assigned to flows.
\item Communication overhead (number of messages exchanged between controllers) for setting up routes for flows.   
\end{itemize}

\begin{center}
\includegraphics[scale=0.3]{msg}
\captionof{figure}{Per flow communication overhead}
\label{fig:msg}
\end{center}

\begin{multicols}{2}
\begin{minipage}{.5\textwidth}
\begin{center}
\includegraphics[scale=0.2]{path.png}
\captionof{figure}{Path length}
\label{fig:path}
\end{center}
\end{minipage}

\begin{minipage}{.5\textwidth}
\begin{center}
\includegraphics[scale=0.2]{util.png}
\captionof{figure}{Maximum link utilization}
\label{fig:util}
\end{center}
\end{minipage}
\end{multicols}
